---
title: "WebScraping"
author: "Vladyslav Pavytskyi"
date: "2023-11-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(rvest)
library(tidyverse)
library(purrr)
library(dplyr)
```


```{r}
url <- "https://www.imdb.com/list/ls027433291/"
page <- read_html(url)


film_name <- page %>% 
  html_nodes(".lister-item-header a") %>% 
  html_text()

year <- page %>% 
  html_nodes(".lister-item-year.text-muted.unbold") %>% 
  html_text() %>% 
  parse_number()

duration <- page %>% 
  html_nodes(".runtime") %>% 
html_text()
```


```{r}
missing_values_function <- function(x,selector){
  specific_node <- html_node(x,selector)
  if(is.null(specific_node)){
    return(NA_character_)
  }else{
    return(html_text(specific_node,trim = TRUE))
  }
}
```


```{r}
film_summary <- page %>% html_nodes(".lister-item.mode-detail")


duration <- map_chr(film_summary,function(x) missing_values_function(x,".runtime"))
duration <- parse_number(duration)

Dataframe <- data.frame(film_name,year,duration)
names(Dataframe) <- c("Name","Year","Duration")

write.csv(Dataframe, file = "DataFrame.csv", row.names = FALSE)
```


# TABELA

```{r}
url_table <- "https://pl.wikipedia.org/wiki/Mistrzostwa_świata_w_piłce_nożnej_mężczyzn"
page_table <- read_html(url_table)


table_team <- page_table %>% 
  html_nodes("table.wikitable.sortable") %>% 
  html_table() %>% 
  .[[2]]

Dataframe_table <- data.frame(table_team)
```


# OTOMOTO CARS

```{r}
car_volkswagen <- "https://www.otomoto.pl/osobowe/volkswagen"
car_page <- read_html(car_volkswagen)

car_title <- car_page %>% html_nodes("article.ooa-1t80gpj.ev7e6t818")

car_name <- map_chr(car_title,function(x) missing_values_function(x,"h1.ev7e6t89.ooa-1xvnx1e.er34gjf0"))

Mileage <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'mileage']"))
Mileage <- parse_number(Mileage)

Fuel_type <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'fuel_type']"))

Gearbox <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'gearbox']"))

Year <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'year']"))
Year <- parse_number(Year)

Place <- map_chr(car_title,function(x) missing_values_function(x,"p.ooa-gmxnzj"))

Price <- map_chr(car_title,function(x) missing_values_function(x,"h3.ev7e6t82.ooa-bz4efo.er34gjf0"))

Dataframe_cars <- data.frame(car_name,Mileage,Fuel_type,Gearbox,Year,Place,Price)
names(Dataframe_cars) <- c("Name","Mileage","Fuel_type","Gearbox","Year","Place","Price")


library(stringr)

Dataframe_cars$Price <- as.numeric(gsub(" ","",Dataframe_cars$Price))
Dataframe_cars$Place <- str_extract_all(Dataframe_cars$Place, "(?<=\\().*?(?=\\))")
Dataframe_cars <- na.omit(Dataframe_cars)

row.names(Dataframe_cars) <- NULL
View(Dataframe_cars)

```



```{r}
Dataframe_Volkswagen <- data.frame()

base_link = "https://www.otomoto.pl/osobowe/volkswagen?page="

for(link in paste0(base_link,2:10)){
  subpage <- read_html(link)
  
  car_title <- subpage %>% html_nodes("article.ooa-1t80gpj.ev7e6t818")
  
  car_name <- map_chr(car_title,function(x) missing_values_function(x,"h1.ev7e6t89.ooa-1xvnx1e.er34gjf0"))

  Mileage <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'mileage']"))
Mileage <- parse_number(Mileage)

  Fuel_type <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'fuel_type']"))

Gearbox <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'gearbox']"))

Year <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'year']"))
Year <- parse_number(Year)

Place <- map_chr(car_title,function(x) missing_values_function(x,"p.ooa-gmxnzj"))

Price <- map_chr(car_title,function(x) missing_values_function(x,"h3.ev7e6t82.ooa-bz4efo.er34gjf0"))

Dataframe<- data.frame(car_name,Mileage,Fuel_type,Gearbox,Year,Place,Price)
Dataframe_Volkswagen <- bind_rows(Dataframe_Volkswagen,Dataframe)

}
Dataframe_Volkswagen$Price <- as.numeric(gsub(" ","",Dataframe_Volkswagen$Price))
Dataframe_Volkswagen$Place <- str_extract_all(Dataframe_Volkswagen$Place, "(?<=\\().*?(?=\\))")
Dataframe_Volkswagen <- na.omit(Dataframe_Volkswagen)

row.names(Dataframe_Volkswagen) <- NULL
View(Dataframe_Volkswagen)

```

```{r}
#write.csv(Dataframe_Volkswagen, file = "DataFrame_volksvagen.csv", row.names = FALSE)
```



```{r}
library(Rcrawler)
```



```{r}
link <- "https://www.imdb.com/title/tt4589218/?ref_=chtmvm_t_1"

test <- Rcrawler(link,dataUrlfilter = "name", MaxDepth = 1)

web_crawling_specific_urls <- INDEX$Url

for(specific_website in web_crawling_specific_urls){
  print(specific_website)
}
```



```{r}
library(rvest)
library(tidyverse)
car_volkswagen <- "https://www.otomoto.pl/osobowe/volkswagen"

car_page<- read_html(car_volkswagen)

cars_specific_information <- car_page %>% html_nodes("h1.ev7e6t89.ooa-1xvnx1e.er34gjf0 a") %>% 
html_attr("href")

cars_specific_information_list <- as.list(cars_specific_information)

for(i in cars_specific_information_list){
  print(i)
}
```




```{r}
base_link <- "https://www.otomoto.pl/osobowe/volkswagen"

Car_links_detail_information <- c()

for(link in paste0(base_link,2:5)){
  subpage <- read_html(link)
  
  cars_specific_information <- subpage %>% html_nodes("h1.ev7e6t89.ooa-1xvnx1e.er34gjf0 a") %>% 
  html_attr("href")
  
  cars_specific_information_list <- as.list(cars_specific_information)
  
  Car_links_detail_information <- append(Car_links_detail_information, cars_specific_information_list)
}
```

car_volkswagen <- "https://www.otomoto.pl/osobowe/volkswagen"
car_page <- read_html(car_volkswagen)

car_title <- car_page %>% html_nodes("article.ooa-1t80gpj.ev7e6t818")

car_name <- map_chr(car_title,function(x) missing_values_function(x,"h1.ev7e6t89.ooa-1xvnx1e.er34gjf0"))

Mileage <- map_chr(car_title,function(x) missing_values_function(x,"dd[data-parameter = 'mileage']"))
Mileage <- parse_number(Mileage)

```{r}
missing_values_function <- function(x,selector){
  specific_node <- html_node(x,selector)
  if(is.null(specific_node)){
    return(NA_character_)
  }else{
    return(html_text(specific_node,trim = TRUE))
  }
}
```


```{r}
filmweb_link <- "https://www.filmweb.pl/ranking/netflix"
film_page<- read_html(filmweb_link)

film_title1 <- film_page %>% html_nodes("div.rankingType.hasVod.rankingType--odd")
film_title2 <- film_page %>% html_nodes("div.rankingType.hasVod.rankingType--even")

film_title <- c(film_title1,film_title2)

position <- map_chr(film_title,function(x) missing_values_function(x,"span.rankingType__position"))
position <- parse_number(position)

nazwa_filmu <- map_chr(film_title,function(x) missing_values_function(x,"h2.rankingType__title"))

ranking <- map_chr(film_title,function(x) missing_values_function(x,"span.rankingType__rate--value"))
ranking<- as.numeric(sub(",",".",ranking))

gatunek <- map_chr(film_title,function(x) missing_values_function(x,"div.rankingType__genres"))
gatunek <- sub("gatunek", "", gatunek)
gatunek <- sub("/.*","",gatunek)

votes <- map_chr(film_title,function(x) missing_values_function(x,"span.rankingType__rate--count"))
votes <- sub(" ocen","",votes)
votes <- sub("y","",votes)
votes <- sub(" ","",votes)
votes <- parse_number(votes)

year <- map_chr(film_title,function(x) missing_values_function(x,"span.rankingType__year"))
year <- parse_number(year)

DataFrame_films <- data.frame(position,nazwa_filmu,ranking,gatunek,votes,year)
names(DataFrame_films) <- c("Position","Nazwa","Rank","Gatunek","Głosy","Year")
View(DataFrame_films)



```


```{r}
ggplot(DataFrame_films, aes(x = gatunek, y = count(gatunek), fill = gatunek)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Najczęstsze gatunki", x = "Gatunek", y = "Liczba wystąpień") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```












```{r}
vector_1 <- c(1,2,3)
vector_2 <- c(4,5)

#Data <- data.frame(vector_1,vector_2)

tryCatch(
  {Dataframe <- data.frame(vector_1,vector_2)},
  error = function(e)
  {print(paste("Error:",e$message))}
)
print("Hey.")
```





